|

### 2019-08-15 article/article.Rmd
results, discussion

We use the TDP app to conduct two experimental interventions and test its impact on six outcomes related to school completion rates and complaints to public authorities. Overall, our results show that providing information to citizens has very limited impact on policy outcomes. We find that the TDP app increased the likelihood of school completion by 6.8 percent in the first experiment, but the effect is null in the second intervention. We also find that pressure over the bureaucracy increased by 157.5 percent in our second experiment, although not in the first. Importantly, our two interventions have no significant impact on any of the other measures of school investment and completion rates we employed in this study.

@@

# Aux function
calcATEs <- function(outcs, treats, ctrls, fes, cls, dat, wts = NULL, ...) {
  ctrls_mod <- paste(ctrls, collapse = '+')
  fes_mod <- paste(fes, collapse = '+')
  moddescr <- data.frame()
  mods <- list()
  if(is.null(wts)) {
    dat <- dat %>%
      select(one_of(c(outcs, treats, ctrls, fes, cls))) %>%
      na.omit()
  } else {
    dat <- dat %>%
      select(one_of(c(outcs, treats, ctrls, fes, cls, wts))) %>%
      na.omit()
    wts <- dat[,wts]
  }
  k <- 1
  for (i in treats) {
    for (j in outcs) {
      # No controls and no fes
      mods[[k]] <- felm(as.formula(
        paste(c(j,paste(i,paste('',0,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wts)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = F,
                                   hFEs = F))
      print(k); k = k+1
      # Controls and no fes
      mods[[k]] <- felm(as.formula(
        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
                        paste('',0,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wts)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = T,
                                   hFEs = F))
      print(k); k = k+1
      # No controls and fes
      mods[[k]] <- felm(
        as.formula(paste(c(j,paste(paste(c(i), collapse = '+'),
                                   paste('',fes_mod,0,cls, sep = '|'), sep = '')),
                         collapse = '~')), data = dat, weights = wts)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = F,
                                   hFEs = T))
      print(k); k = k+1
      # Controls and fes
      mods[[k]] <- felm(as.formula(
        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wts)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = T,
                                   hFEs = T))
      print(k); k = k+1
    }
  }
  return(list(moddescr, mods))
}

@@

@@

\vspace{.5cm}
**TABLE 1 ABOUT HERE: RESULTS INTERVENTION 1**
\vspace{.5cm}

@@

\vspace{.5cm}
**TABLE 2 ABOUT HERE: RESULTS INTERVENTION 2**
\vspace{.5cm}

We observe a similar pattern in the second intervention. Table \ref{tab:results2} shows that the treatment does not have a statistically significant effect on any our outcomes of interest, including the placebo. This provides evidence that our previous findings are not a statistical fluke, and questions the robustness of the effect of the TDP app on school completion. Nevertheless, in our additional tests we find that the app improved the difference between the baseline and the end-line reported investment by 157.5 percent. This is a large effect, yet it only reaches statistical significance when we employ inverse probability weights with block randomization and one-to-one nearest neighbourhood matching.

Figure \ref{fig:permtest} shows the results of our randomisation inference tests. Randomisation inference allows us to estimate the probability of the sharp null hypothesis over all possible randomisations that could have occurred under our research design [@coppock2019ri2; @gerber2012field].

>>>>

We use the TDP app to conduct two experimental interventions and test its impact on six outcomes related to school completion rates and complaints to public authorities. Overall, our results show that providing information to citizens has very limited impact on policy outcomes. We find that the TDP app increased the likelihood of school completion by 6.8 percent in the first experiment, but the effect is null in the second intervention. We also find that the app increased the percentage of the executed budget by 157.5 percent in our second experiment, but only after nearest neighbourhood matching adjustment. No result reported in the first intervention or in the unmatched sample. Importantly, both interventions have no significant impact on any of the other measures of school investment and completion rates we employed in this study.

@@

# Load packages
pkgs <- c('tidyverse', 'dummies', 'kableExtra',
          'haven', 'compareGroups', 
          'devtools', 'lubridate', 'brazilmaps',
          'abjutils', 'lfe', 'cobalt', 
          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
          'flextable', 'officer')
invisible(lapply(pkgs, require, character.only = T))

@@

# Load packages
pkgs <- c('tidyverse', 'dummies', 'kableExtra',
          'haven', 'compareGroups', 
          'devtools', 'lubridate', 'brazilmaps',
          'abjutils', 'lfe', 'cobalt', 
          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
          'flextable', 'officer')
invisible(lapply(pkgs, require, character.only = T))

@@

```{r model1, echo=FALSE, warning=FALSE, message=FALSE, results='hide', cache=TRUE}
load('tdp.RData')

# Load packages
pkgs <- c('tidyverse', 'dummies', 'kableExtra',
          'haven', 'compareGroups', 
          'devtools', 'lubridate', 'brazilmaps',
          'abjutils', 'lfe', 'cobalt', 
          'MatchIt', 'ri2', 'DeclareDesign', 'knitr',
          'DiagrammeR', 'DiagrammeRsvg', 'rsvg', 
          'flextable', 'officer')
invisible(lapply(pkgs, require, character.only = T))

# Auxiliary function: calculate coefficients
calcATEs <- function(outcs, treats, ctrls, fes, cls, dat, wts = NULL, ...) {
  ctrls_mod <- paste(ctrls, collapse = '+')
  fes_mod <- paste(fes, collapse = '+')
  moddescr <- data.frame()
  mods <- list()
  if(is.null(wts)) {
    dat <- dat %>%
      select(one_of(c(outcs, treats, ctrls, fes, cls))) %>%
      na.omit()
  } else {
    dat <- dat %>%
      select(one_of(c(outcs, treats, ctrls, fes, cls, wts))) %>%
      na.omit()
    wts <- dat[,wts]
  }
  k <- 1
  for (i in treats) {
    for (j in outcs) {
      # No controls and no fes
      mods[[k]] <- felm(as.formula(
        paste(c(j,paste(i,paste('',0,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wts)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = F,
                                   hFEs = F))
      print(k); k = k+1
      # Controls and no fes
      mods[[k]] <- felm(as.formula(
        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
                        paste('',0,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wts)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = T,
                                   hFEs = F))
      print(k); k = k+1
      # No controls and fes
      mods[[k]] <- felm(
        as.formula(paste(c(j,paste(paste(c(i), collapse = '+'),
                                   paste('',fes_mod,0,cls, sep = '|'), sep = '')),
                         collapse = '~')), data = dat, weights = wts)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = F,
                                   hFEs = T))
      print(k); k = k+1
      # Controls and fes
      mods[[k]] <- felm(as.formula(
        paste(c(j,paste(paste(c(i,ctrls_mod), collapse = '+'),
                        paste('',fes_mod,0,cls, sep = '|'), sep = '')),
              collapse = '~')), data = dat, weights = wts)
      moddescr <- rbind(moddescr, 
                        data.frame(outc = j, 
                                   treat = i,
                                   hCtrls = T,
                                   hFEs = T))
      print(k); k = k+1
    }
  }
  return(list(moddescr, mods))
}

####
## Analysis Intervention 1
####

## ATEs 
outcs <- c('percExecBegin', 'percExecEnd',
           'deltaPercExec', 'isFinished',
           'isCancelled', 'updDate')
treats <- c('treat')
ctrls <- c('logPop2015', 'ideb_ai_2015','ideb_af_2015',
           'log_poorFam2010', 'log_totTransf2016')
fes <- c('state')
cls <- c('municipality')

resInt1 <- calcATEs(outcs, treats, ctrls, fes, cls, dat = impEvalph1)
```

```{r results1, results='asis', echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE}
# Results intervention 1
library(stargazer)
stargazer(resInt1[[2]][[4]],resInt1[[2]][[8]],resInt1[[2]][[12]],
          resInt1[[2]][[16]],resInt1[[2]][[20]],resInt1[[2]][[24]],
          title = 'Impact Evaluation -- Intervention 1', 
          keep='treatTreatment', type = 'latex',
          covariate.labels = 'ATE',
          column.labels = c('Investment\\\\ Before','Invest\\\\ After',
                             'Delta\\\\ Investment','Finished\\\\ Construction',
                             'Cancelled\\\\ Construction','Updated\\\\ Date'),
          dep.var.labels.include=F,
          omit.stat=c('adj.rsq', 'ser'), style='apsr',
          align=F, digits=2,
          notes = 'Cluster-robust SEs at the municipal level.',
          notes.append = T, header=FALSE)
```

@@

We observe a similar pattern in the second intervention. Table \ref{tab:results2} shows that the treatment does not have a statistically significant effect on any our outcomes of interest, including the placebo. This provides evidence that our previous findings are not a statistical fluke, and questions the robustness of the effect of the TDP app on school completion. Nevertheless, in our additional tests we find that the app improved the difference between the baseline and the end-line reported investment by 157.5 percent. This is a large effect, yet it only reaches statistical significance when we employ inverse probability weights with block randomization and one-to-one nearest neighbourhood matching. The result is in the Supplementary Material.

```{r table3, echo=FALSE, warning=FALSE, message=FALSE}
```

Figure \ref{fig:permtest} shows the results of our randomisation inference tests. Randomisation inference allows us to estimate the probability of the sharp null hypothesis over all possible randomisations that could have occurred under our research design [@coppock2019ri2; @gerber2012field]. We fail to reject the null in all specifications.

We also note that the effect sizes are notably small in each of all our original models. Therefore, even if the treatment effects were statistically significant, the TDP app would have a reduced impact over the outcomes. This has an important substantive meaning, as it poses a direct challenge to the bottom-up accountability theory, at least for the school construction outcomes we estimated here.
